Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-15 exp1/present2013.tex
some math additions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@678 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

\begin{block}{Examples}
  \begin{itemize}
  \item Which concrete implementation
  \item Which Hardware platform
  \item Number of triples in the store
  \item Absence or presence of certain language features
  \item Order of experiments
  \item Level of concurrency
  \end{itemize}
\end{block}

\begin{block}{For the mathematically inclined}
  The response variable is itself a function $R \( a, b, c, \ldots
  \)$, where $a$, $b$, $c$ are factors.
\end{block}

@@

\begin{itemize}
\item Similarities to regression.
\item \emph{Main effects} consider the factors on their own.
\item \emph{Interaction effects} consider factors given levels of
  other factors.
\item In practice done with linear regression routines.
\end{itemize}

@@

  \begin{itemize}
  \item Different strategies must be tried, open field.
  \item Parameterization is very important.
    \begin{itemize}
    \item Data heterogeneity, skewed distributions, etc.
    \item Parameterizing SPARQL queries, see e.g. SPLODGE by Görlitz
      et al.
    \item Parameterizing SPARQL queries using the grammar pragmatically?
    \end{itemize}
  \end{itemize}

>>>>

  \begin{block}{Message for the takeaway}
    If you develop techniques for performance enhancements of complex
    systems, you need to think carefully about how you prove that 
    you've achieved something of general validity. 
  \end{block}

@@

\begin{block}{Examples}
  \begin{itemize}
  \item Which concrete implementation
  \item Which hardware platform
  \item Number of triples in the store
  \item Absence or presence of certain language features
  \item Order of experiments
  \item Level of concurrency
  \end{itemize}
\end{block}

\begin{block}{For the mathematically inclined}
  The response variable is itself a function 
  $R ( A, B, C, \ldots ) $, 
  where $A$, $B$, $C$ etc. are factors.
\end{block}

@@

\begin{itemize}
\item Similarities to regression.
\item \emph{Main effects} consider the factors on their own.
\begin{block}{For the mathematically inclined}
  $ME(A) = \bar{z}(A_2) - \bar{z}(A_1)$ where $\bar{z}(A_n)$ is the
  average of all values observed for factor $A$ at level $n$.
\end{block}

\item \emph{Interaction effects} consider factors given levels of
  other factors.
\item In practice done with linear regression routines.
\end{itemize}

@@

  \begin{itemize}
  \item Different strategies must be tried, open field.
  \item Formal methods from AI?
  \item Parameterization is very important.
    \begin{itemize}
    \item Data heterogeneity, skewed distributions, etc.
    \item Parameterizing SPARQL queries, see e.g. SPLODGE by Görlitz
      et al.
    \item Parameterizing SPARQL queries using the grammar pragmatically?
    \end{itemize}
  \end{itemize}
